---
title: "Multi100: Raw to processed data cleaning"
format: html
editor_options: 
  chunk_output_type: console
---

## Setup
### Loading packages

```{r}
library(tidyverse)
```

### Load custom functions

```{r}
source(here::here("R/utils.R"))
source(here::here("R/standard_correlation_coefficient.R"))
source(here::here("R/cohens_d.R"))
```

## Read data

```{r}
# Task1 form responses
task1 <- readr::read_csv(here::here("data/raw/multi100_task1_raw_data.csv"))

# Task2 form responses
task2 <- readr::read_csv(here::here("data/raw/multi100_task2_raw_data.csv"))

# 'all_people' data (to be used for checking that ID's match)
all_people <- readr::read_csv(here::here("data/raw/multi100_all-people_raw_data.csv"))

# 'all_paper' meta-information on all papers analyzed
all_paper <- readr::read_csv(here::here("data/raw/multi100_all-paper_raw_data.csv"))

# Master spreadsheet
master <- readr::read_csv(here::here("data/raw/multi100_master_raw_data.csv"))

# Original effect sizes
original_effect_sizes <- readr::read_csv(here::here("data/raw/multi100_original-effect-sizes_raw_data.csv"))

# Reanalyzes effect sizes
reanalyzed_effect_sizes <- readr::read_csv(here::here("data/raw/multi100_reanalyzed-effect-sizes_raw_data.csv"))

# Peer evaluation data
peer_eval <- readr::read_csv(here::here("data/raw/multi100_peer-eval_raw_data.csv"))

# Peer evaluation review data
peer_eval_review <- readr::read_csv(here::here("data/raw/multi100_peer-eval-review_raw_data.csv"))

# Reviewing the direction of the claims in task2
claim_direction_review <- readr::read_csv(here::here("data/raw/multi100_claim-direction-review_raw_data.csv"))

# Non-detailed responses
non_detailed_responses <- readr::read_csv(here::here("data/raw/multi100_non-detailed-responses_raw_data.csv"))
```

## all_paper

```{r}
all_paper <-
  all_paper |> 
  # Excluding empty rows
  filter(if_any(everything(), ~!is.na(.x))) |> 
  mutate(
     # Remove leading and trailing spaces from paper_id
    paper_id = trimws(paper_id, "both"),
    # Reformatting short references for the papers
    original_paper_reference = str_replace(original_paper_reference, "_(?=[^_]*$)", ", "),
    original_paper_reference = str_replace(original_paper_reference, "_etal", " et al."),
    original_paper_reference = str_replace(original_paper_reference, "&", " & ")
    )
```

Check if all paper_id has a corresponding original_paper_reference.

```{r}
all_paper |> 
  filter(is.na(original_paper_reference)) |> 
  nrow()
```

Number of papers in all_paper based on paper_id, it should be a 100.

```{r}
all_paper |> 
  distinct(paper_id) |> 
  nrow()
```

## all_people

Check if analysts have only one analyst_id.

```{r}
all_people |> 
  distinct(first_name, last_name, analyst_id) |>  
  group_by(first_name, last_name) |> 
  mutate(n_analyst_id = n()) |> 
  arrange(desc(n_analyst_id), last_name)
```

Check if analyst_id is unique to the person.

```{r}
all_people |> 
  distinct(first_name, last_name, analyst_id) |> 
  group_by(analyst_id) |> 
  mutate(n_analyst_id = n()) |> 
  arrange(desc(analyst_id))
```

Check who agreed to have their name attached to the analysis.

```{r}
all_people |> 
  count(name_attached_to_analysis)
```

## original_effect_sizes

Select needed variables.

```{r}
original_effect_sizes <-
  original_effect_sizes |> 
  dplyr::select(-original_materials)
```

Effect sizes were calculated in excel for this table. The decimal place is denoted with a comma instead of a dot. We change that now.

We also convert all the original effect sizes positive.

```{r}
original_effect_sizes <-
  original_effect_sizes |> 
  mutate(
    original_correlation_coef = as.numeric(original_correlation_coef),
    original_cohens_d = abs(as.numeric(original_cohens_d))
  )
```

## reanalyzed_effect_sizes

Select variables needed.

```{r}
reanalyzed_effect_sizes <-
  reanalyzed_effect_sizes |> 
  dplyr::select(
    analyst_id,
    paper_id,
    reanalysis_es_missing,
    reanalysis_es_missing_reason,
    reanalysis_type_of_statistic,
    reanalysis_statistic_report,
    reanalysis_degrees_of_freedom_1,
    reanalysis_degrees_of_freedom_2,
    reanalysis_model_sample_size
  ) %>%
  mutate(
    # Filling in variables with NAs to make values explicit
    reanalysis_es_missing = case_when(
      is.na(reanalysis_es_missing) ~ 0L,
      !is.na(reanalysis_es_missing) ~ reanalysis_es_missing
    )
  )
```

Check if there are duplicate responses in the reanalyzed effect sizes.

```{r}
reanalyzed_effect_sizes |> 
  count(paper_id, analyst_id) |> 
  filter(n > 1) |> 
  arrange(desc(n))
```

Delete the duplicate response.

```{r}
reanalyzed_effect_sizes <-
  reanalyzed_effect_sizes |> 
  filter(!(analyst_id == "JX7YO" & paper_id == "Christensen_EurJournPersonality_2018_8R9d" & reanalysis_statistic_report == "0.132"))
```

Calculate the Cohen's ds for the reanalyses.

```{r}
reanalysis_vars <- c("reanalysis_type_of_statistic", "reanalysis_statistic_report", "reanalysis_model_sample_size", "reanalysis_degrees_of_freedom_1", "reanalysis_degrees_of_freedom_2")

reanalyzed_effect_sizes <-
  reanalyzed_effect_sizes |> 
  mutate(reanalysis_type_of_statistic = str_replace_all(reanalysis_type_of_statistic, "²", "2")) |> 
  mutate(
    across(
      all_of(reanalysis_vars),
      ~ if_else(reanalysis_es_missing == 1L, NA, .)
      )
    ) |> 
  mutate(
    across(
      all_of(c("reanalysis_statistic_report", "reanalysis_model_sample_size", "reanalysis_degrees_of_freedom_1", "reanalysis_degrees_of_freedom_2")),
      ~ as.numeric(.)
      )
  )

reanalyzed_effect_sizes <-
  reanalyzed_effect_sizes %>%
  mutate(
    reanalysis_statistic_report = dplyr::case_when(
      reanalysis_type_of_statistic == "F" ~ abs(reanalysis_statistic_report),
      TRUE ~ reanalysis_statistic_report
    ),
    reanalysis_correlation_coef = mapply(
      standard_correlation_coefficient,
      type_of_statistic = reanalysis_type_of_statistic,
      test_statistic = reanalysis_statistic_report,
      sample_size = reanalysis_model_sample_size,
      df1 = reanalysis_degrees_of_freedom_1,
      df2 = reanalysis_degrees_of_freedom_2,
      reanalysis_es_missing = reanalysis_es_missing,
      SIMPLIFY = TRUE  # Ensure results are simplified if applicable
    ),
    reanalysis_cohens_d = cohens_d(
      r = reanalysis_correlation_coef,
      # Used for calculating cohens d for regression coefficients
      type_of_statistic = reanalysis_type_of_statistic,
      test_statistic = reanalysis_statistic_report,
      sample_size = reanalysis_model_sample_size
    ),
    # Taking the absolute value of every effect size
    reanalysis_cohens_d = abs(reanalysis_cohens_d)
  )
```

## task1

```{r}
task1 <- 
  task1 |> 
  mutate(
    # add 'task1_submission_number' as a reference variable
    task1_submission_number = 1:nrow(task1),
    # remove leading and trailing spaces from Analyst_ID and Paper_ID variables
    analyst_id = trimws(analyst_id, "both"),
    paper_id = trimws(paper_id, "both"),
    # rewrite inference categorization labels
    task1_categorisation_plotting = case_when(
      task1_categorisation == "The results show evidence for the relationship/effect as described in the claim provided in your task" ~ "Same conclusion",
      task1_categorisation %in% c(
        "The results do not show evidence for or against the relationship/effect as described in the claim provided in your task",
        "The results show evidence for the null-hypothesis"
        ) ~ "No effect/inconclusive",
      task1_categorisation == "The results show evidence for opposite relationship/effect as described in the claim provided in your task" ~ "Opposite effect",
      TRUE ~ NA_character_)
  )
```

We are excluding the pilot responses. Analysts with analyst_id "8nJioy5V5B" and "z2u1wLLVu1" are test runs (pilot data).

```{r}
task1 <-
  task1 |> 
  filter(analyst_id %ni% c("8nJioy5V5B", "z2u1wLLVu1"))
```

Check whether the paper_id provided by the analyst matches the correct id.
Check if all paper_id's in 'task1' are present in 'all_paper', if 'FALSE' then ID's match.

```{r}
any(!(task1$paper_id %in% all_paper$paper_id))
```

Found non-matching paper_id's. Print paper_id values in 'task1' that are not present in 'all_paper'.

```{r}
task1$paper_id[!task1$paper_id %in% all_paper$paper_id]
```

Correcting the erroneous paper_id's:
* 'XAS95 Raley_JournMarFam_2012_D2LY' should be 'Raley_JournMarFam_2012_D2LY'
* 'Rjp9' should be 'Jiang_AmJourPoliSci_2018_Rjp9'

```{r}
task1 <-
  task1 |> 
  mutate(paper_id = case_when(
    paper_id == "XAS95 Raley_JournMarFam_2012_D2LY" ~ "Raley_JournMarFam_2012_D2LY",
    paper_id == "Rjp9" ~ "Jiang_AmJourPoliSci_2018_Rjp9",
    TRUE ~ paper_id
  ))
```

Verify that all paper_ids are now present.

```{r}
any(!(task1$paper_id %in% all_paper$paper_id))
```

Check how many analyses were submitted with '_2' ID's. Some analyst submitted multiple analyses. We assigned '_2' to the analyst_ids of these analyst for the second and possibly third analyses.

```{r}
task1_multiple_analyses <- 
  task1 |> 
  filter(str_detect(analyst_id, "_")) |> 
  dplyr::select(analyst_id, paper_id) |> 
  arrange(analyst_id) |> 
  group_by(analyst_id) |> 
  mutate(n = n())
```

There are no analysts who did more than 2 analysis.

We are removing '_2' from the end of analyst_id's in both Task 1 and Task 2. They are not needed for further analysis because paper_id and analyst_id together can identify an analysis perfectly.

```{r}
task1 <-
  task1 |> 
  mutate(analyst_id = str_replace(analyst_id, "_2$", ""))
```

Check whether each analyst_id matches with the ID they were assigned in the signup form ('all_people').
Check if all analyst_id in task1 are present in all_people, if 'FALSE' then all ID's match.

```{r}
any(!(task1$analyst_id %in% all_people$analyst_id)) 
```

Check for duplicate responses.

```{r}
task1_duplicates <-
  task1 |> 
  group_by(paper_id, analyst_id) |> 
  mutate(n = n()) |> 
  filter(n > 1) |> 
  arrange(desc(n))

task1_duplicates |> 
  distinct(paper_id, analyst_id, n)
```

Attend to each of these cases manually. We will only keep the correct responses for further analysis.

```{r}
task1 <-
  task1 |> 
  filter(
   # GNUQA_GROSSMAN
    # SN. 23 to be removed... responses largely identical, but the comments of the analyst indicate that SN. 24 is their preferred version
    task1_submission_number != 23,
    # KZGB8_Ku
    # SN. 25 to be removed... analyst forgot to include something in original
    task1_submission_number != 25,
    # AJIUW_Angrist
    # SN. 64 to be removed... submission is identical apart from conclusion... consider duplicate response a replacement of the original
    task1_submission_number != 64,
    # 419LV_Bursztyn
    # SN. 110 to be removed... submission is identical apart from 'years of experience'... 
    # SN. 110 states that the analyst is 30 years old and has 30 years of experience. SN. 108 reports 6 years of experience...
    # consider SN. 110 an error
    task1_submission_number != 110,
    # T6S8L_Robertson
    # SN. 193 to be removed... original submission states the claim cannot be tested, but the duplicate SN. 235 corrects this
    task1_submission_number != 193,
    # YMESM_Cohen
    # SN. 91 to be removed... SN. 237 is stated as an updated entry
    task1_submission_number != 91,
    # IFVKR_Robertson
    # SN. 52 to be removed... SN. 250 is an updated entry
    task1_submission_number != 52,
    # 5GT7K_Wlezien
    # SN. 49 to be removed... SN. 282 is an updated entry
    task1_submission_number != 49,
    # XF5GJ_Wlezien
    # SN. 146 to be removed... SN. 283 is an updated entry
    task1_submission_number != 146,
    # KNXVJ_Wlezien
    # SN. 216 to be removed... SN. 284 is an updated entry
    task1_submission_number != 216,
    # YEJO9_Andreoni
    # SN. 316 to be removed... SN. 324 is stated as an updated entry
    task1_submission_number != 316,
    # J5BBA_Caldero
    # SN. 337 to be removed... SN. 345 is an updated entry
    task1_submission_number != 337,
    # 8AYYN_Menaldo
    # SN. 378 + 379 to be removed... three identical submissions
    task1_submission_number != 378,
    task1_submission_number != 379,
    # K0XHI_Platt
    # SN. 386 + 387 to be removed... SN. 388 states that this is their third and final submission with minor changes made from the previous
    task1_submission_number != 386,
    task1_submission_number != 387,
    # HDP26_Cleave
    # SN. 498 to be removed... SN. 497 is stated as an updated entry
    task1_submission_number != 498,
    # K9J6C_Hendricks
    # SN. 415 to be removed... SN. 536 is an updated entry
    task1_submission_number != 415 
  )
```

Verify that there are no longer any duplicates.

```{r}
task1 |> 
  count(paper_id, analyst_id) |> 
  filter(n > 1)
```

Replace the non-detailed responses about the analysis procedure with additional information provided by the analyst as a response to our follow-up questions.

```{r}
task1_change_from <-
  non_detailed_responses |> 
  filter(variable_identified_in == "task1_analysis_report") |> 
  dplyr::select(paper_id, analyst_id, change_to)

task1 <-
  task1 |> 
  left_join(task1_change_from, by = c("paper_id", "analyst_id")) |> 
  mutate(task1_analysis_report = case_when(
    !is.na(change_to) ~ change_to,
    TRUE ~ task1_analysis_report   
  )) |> 
  dplyr::select(-change_to)
```

## Task 2

```{r}
task2 <- 
  task2 |> 
  mutate(
    # add 'task2_submission_number' as a reference variable
    task2_submission_number = 1:nrow(task2),
    # remove leading and trailing spaces from Analyst_ID and Paper_ID variables
    analyst_id = trimws(analyst_id, "both"),
    # Remove '_2' from the 'analyst_id' variable
    analyst_id = str_replace(analyst_id, "_2$", ""),
    paper_id = trimws(paper_id, "both")
  )
```

Check whether each analyst_id matches with the ID they were assigned in the signup form ('all_people').
Check if all analyst_id in task2 are present in all_people, if 'FALSE' then all ID's match.

```{r}
any(!(task2$analyst_id %in% all_people$analyst_id)) 
```

Find non-matching analyst_ids in task2 that are not present in the submission form.

```{r}
anti_join(task2, all_people, by = "analyst_id")
```

Replacing non-matching analyst_ids.

```{r}
task2 <- 
  task2 |> 
  mutate(analyst_id = case_when(
    # PGT48 should be PTG48
    analyst_id == "PGT48" ~ "PTG48",
    # h46k4 should be H46K4
    analyst_id == "h46k4" ~ "H46K4",
    # CO9RR should be C09RR (zero rather than capital o)
    analyst_id == "CO9RR" ~ "C09RR",
    TRUE ~ analyst_id
  ))
```

Verify that there are no missing analyst_ids.

```{r}
anti_join(task2, all_people, by = "analyst_id")
```

Both Task1 and Task2 analyst_ids's now match with the ID they were assigned to.

Check whether the paper_id provided by the analyst matches the correct paper_id in the meta-information sheet provided by OSF.

```{r}
any(!(task2$paper_id %in% all_paper$paper_id))
```

Find non-matching paper_ids. Find paper_id values in 'task2' that are not present in 'all_paper'.

```{r}
task2$paper_id[!task2$paper_id %in% all_paper$paper_id]
```

Correcting the erroneous paper_id's:
* 'Tenye_EurSocioRev_2016_qXX2' should be 'Teney_EurSocioRev_2016_qXX2'
* 'qQ9Z' should be 'Desmond_Demography_2015_qQ9Z'
* 'RJP9' should be 'Jiang_AmJourPoliSci_2018_Rjp9'

```{r}
task2 <-
  task2 |> 
  mutate(paper_id = case_when(
    paper_id == "Tenye_EurSocioRev_2016_qXX2" ~ "Teney_EurSocioRev_2016_qXX2",
    paper_id == "qQ9Z" ~ "Desmond_Demography_2015_qQ9Z",
    paper_id == "RJP9" ~ "Jiang_AmJourPoliSci_2018_Rjp9",
    TRUE ~ paper_id
  ))
```

Verify that all paper_ids are now present.

```{r}
any(!(task2$paper_id %in% all_paper$paper_id))
```

"JX7YO" wrongly submitted Task 2 paper_id as McLaren... should be Christensen... We rectify that now.

```{r}
task2 <-
  task2 |> 
  mutate(paper_id = case_when(
    analyst_id == "JX7YO" & paper_id == "McLaren_WorldPolitics_2012_wRvv" ~ "Christensen_EurJournPersonality_2018_8R9d",
    TRUE ~ paper_id
  ))
```

Check for duplicate responses.

```{r}
task2_duplicates <-
  task2 |> 
  group_by(paper_id, analyst_id) |> 
  mutate(n = n()) |> 
  filter(n > 1) |> 
  arrange(desc(n))

task2_duplicates |> 
  distinct(paper_id, analyst_id, n)
```

There are `r nrow(distinct(task2_duplicates, paper_id, analyst_id, n))` analyses where there are duplicate responses out of the `r nrow(task2)` responses. Since in some cases there are more than 2 responses, after deleting the duplicates `r nrow(task2) - (nrow(task2_duplicates) - nrow(distinct(task2_duplicates, paper_id, analyst_id, n)))` responses should remain task2.

Attend to each of these cases manually. Manual inspection of the duplicate responses confirms that the last instance of each analysis is the analysis that should remain in the dataset.

```{r}
task2 <-
  task2 |> 
  mutate(task2_timestamp = ymd_hms(task2_timestamp)) |> 
  group_by(analyst_id, paper_id) %>%
  filter(task2_timestamp == max(task2_timestamp)) |> 
  ungroup()
```

Ensure that all the duplicates are gone.

```{r}
task2 |> 
  group_by(paper_id, analyst_id) |> 
  mutate(n = n()) |> 
  filter(n > 1) |> 
  arrange(desc(n))
```

After deleting the duplicates there are `r nrow(task2)` responses remained. The deletion of the duplicates was successful.

Check how many Analyst ID's are present in Task1 data but NOT Task2 data. Then, verify that there are no analyst_ids in Task2 that do not appear in Task1.

```{r}
# It is possible to have analyst_ids in task1 that are not present in task2, since not all of the analysts completed task2 who completed task2
setdiff(task1$analyst_id, task2$analyst_id) 
# But there should be no analyst who completed task2 but did not submit a task1 response
setdiff(task2$analyst_id, task1$analyst_id)
```

Check the number of distinct papers in task2.

```{r}
task2 |> 
  distinct(paper_id) |> 
  nrow()
```

Replace the non-detailed responses about the analysis procedure with additional information provided by the analyst as a response to our follow-up questions.

```{r}
task2_change_from <-
  non_detailed_responses |> 
  filter(variable_identified_in == "task2_analysis_report") |> 
  dplyr::select(paper_id, analyst_id, change_to)

task2 <-
  task2 |> 
  left_join(task2_change_from, by = c("paper_id", "analyst_id")) |> 
  mutate(task2_analysis_report = case_when(
    !is.na(change_to) ~ change_to,
    TRUE ~ task2_analysis_report   
  )) |> 
  dplyr::select(-change_to)
```

## Combining Task 1 and Task 2

Join task 1 and task 2 data based on both analyst_id and paper_id.

```{r}
multi100_data <- inner_join(task1, task2, by = c("analyst_id", "paper_id"))
```

Check the number of distinct papers based on paper_id after joining task1 and task2 responses. There should be a 100 distinct papers in the dataset.

```{r}
multi100_data |> 
  distinct(paper_id) |> 
  nrow()
```

Check number of analyses based on paper_id.

```{r}
multi100_data |> 
  count(paper_id) |> 
  arrange(desc(n))
```

Check if every analyses are unique.

```{r}
multi100_data |> 
  count(paper_id, analyst_id) |> 
  filter(n > 1)
```

## Combining signup form

Merge all_people with multi100_data based on analyst_id.

```{r}
multi100_data <- inner_join(multi100_data, all_people, by = "analyst_id")
```

## Merge original paper info

Merge with multi100_data based on paper_id

```{r}
multi100_data <- inner_join(multi100_data, all_paper, by = "paper_id")
```

## Merge master spreadsheet

```{r}
multi100_data <- inner_join(multi100_data, master, by = "paper_id")
```

## Merge original effect size info

```{r}
multi100_data <- inner_join(multi100_data, original_effect_sizes, by = "paper_id")
```

## Merge reanalyzes effect size info

Check which multi100 analyses is not in the reanalyzed_effect_sizes table.

```{r}
anti_join(multi100_data, reanalyzed_effect_sizes, by = c("paper_id", "analyst_id"))
# These analyst will be excluded from the main analysis
# We flag them later in the code
```

```{r}
multi100_data <- left_join(multi100_data, reanalyzed_effect_sizes, by = c("paper_id", "analyst_id"))
```

## Select and re-order variables

```{r}
multi100_data <-
  multi100_data |> 
  dplyr::select(
    # id variables
    analyst_id, paper_id,
    # personal information
    first_name, last_name, 
    # operational information for the project
    name_attached_to_analysis, disclosure_agreement, willing_to_peer_eval,
    # timestamps
    signup_timestamp, task1_timestamp, task2_timestamp, 
    # demographic information
    current_position_grouped, education_level, primary_discipline, keywords,
    # experience with analysis
    experience_conducting_analyses, years_of_experience, analysis_frequency, expertise_self_rating, total_hours,
    # familiarity and discussion of the paper
    familiar_with_paper, communication_check,
    # paper level information
    paper_discipline, reproduction_type_osf, reproduction_result_osf, categorisation_of_claim, original_title, original_materials, original_paper_reference, experimental_or_observational, paper_link, general_osf_link,
    # original paper statistical results
    original_claim, in_text_original_statistical_result, related_original_statistical_result,
    original_type_of_statistic, original_statistic_report, original_degrees_of_freedom_1,
    original_degrees_of_freedom_2, original_model_sample_size, original_result_page_number,
    original_correlation_coef, original_cohens_d, original_effect_size_available, original_reproduction_outcome,
    # task1 responses (some of the variables were included before)
    task1_software, task1_analysis_report, task1_conclusion, task1_categorisation, task1_categorisation_plotting, confidence_in_approach,
    data_suitability, instructions_given,
    # task2 responses (some of the variables were included before)
    task2_software, task2_analysis_report,
    # the cleaned versions of these variables are included with reanalaysis_ suffix
    # type_of_statistic,
    # statistic_report,
    # model_sample_size,
    # model_degrees_of_freedom,
    p_value_or_bayes,
    p_value_report, task2_conclusion, direction_of_result, same_statistical_result_as_task1,
    additional_calculations,
    # reproduced effect sizes
    reanalysis_es_missing, reanalysis_es_missing_reason, reanalysis_type_of_statistic, reanalysis_statistic_report, reanalysis_degrees_of_freedom_1, reanalysis_degrees_of_freedom_2, reanalysis_model_sample_size, reanalysis_correlation_coef, reanalysis_cohens_d
    )
```

## Cleaning merged dataset

Add id_number to each analysis.

```{r}
multi100_data <-
  multi100_data |> 
  group_by(paper_id, analyst_id) |> 
  mutate(analysis_id = cur_group_id()) |> 
  ungroup()
```

Change _experimental_or_observational_ values to explicit character type.

```{r}
multi100_data <-
  multi100_data |> 
  dplyr::mutate(
    experimental_or_observational = case_when(
      experimental_or_observational == 1L ~ "experimental",
      experimental_or_observational == 0L ~ "observational",
      TRUE ~ NA_character_
    )
  )
```

View the analyses we have to remove based on the expert review of the peer evaluation.

```{r}
peer_eval_review |> 
  filter(expert_panel_decision == "Remove") |> 
  dplyr::select(analyst_id, paper_id, expert_panel_decision)
```

Flag analyses that we will exclude because they did not pass the peer evaluation or because the analyst did not provide an analysis in their response.

```{r}
multi100_data <-
  multi100_data %>%
  dplyr::mutate(
    peer_eval_pass = case_when(
      # add one more based on harry
      # Based on expert panel decision
      analyst_id == "NSDML" &
        paper_id == "PALER_AmPoliSciRev_2013_Pxp7" ~ FALSE,
      TRUE ~ TRUE
    ),
    # we removed them because they did not actually do the analysis
    incomplete_response_pass = case_when(
      analyst_id == "8P2J2" &
        paper_id == "Dahl_AmEcoRev_2012_VRKK" ~ FALSE,
      analyst_id == "8PTRZ" &
        paper_id == "Baccara_AmEcoJourn_2014_RqVE" ~ FALSE,
      analyst_id == "93K4P" &
        paper_id == "TERTYTCHNAYA_AmPoliSciRev_2018_9wya" ~ FALSE,
      analyst_id == "YZDX0" &
        paper_id == "Lu_JournLabEco_2015_vaWE" ~ FALSE,
      TRUE ~ TRUE
    )
  )
```

Some analyst_ids are not unique to the person. We correct this error now before saving the processed dataset.

The id that we will use for these analysts are:
* Mahmoud Elsherif: EZI7J
* Chris Aberson: N8P2J

```{r}
multi100_data <-
  multi100_data %>%
  mutate(analyst_id = case_when(
    analyst_id == "MX02W" ~ "EZI7J",
    analyst_id == "NFTMG" ~ "N8P2J",
    TRUE ~ analyst_id
  ))
```

Create a simplified paper_id for the figures.

```{r}
multi100_data <-
  multi100_data |> 
  group_by(paper_id) |> 
  mutate(
    simplified_paper_id = stringr::str_pad(dplyr::cur_group_id(), width = 3, pad = "0")
  ) |> 
  ungroup()
```

Change the direction of task2 effect sizes based on the direction of the reanalysis conclusion compared to the original conclusion.

```{r}
multi100_data <-
  multi100_data |> 
  mutate(   
    # All the reanalysed effect sizes are negative where the reanalysed conclusion goes the opposite direction than the original
    reanalysis_cohens_d = if_else(direction_of_result == "Opposite as claimed by the original study",
                                  reanalysis_cohens_d * -1,
                                  reanalysis_cohens_d))
```

Export processed dataframe.

```{r}
write_csv(multi100_data, here::here("data/processed/multi100_processed_data.csv"))
```

Export the rest of the datasets.

```{r}
readr::write_csv(task1, here::here("data/processed/multi100_task1_processed_data.csv"))

readr::write_csv(task2, here::here("data/processed/multi100_task2_processed_data.csv"))

readr::write_csv(all_people, here::here("data/processed/multi100_all-people_processed_data.csv"))

readr::write_csv(all_paper, here::here("data/processed/multi100_all-paper_processed_data.csv"))

readr::write_csv(master, here::here("data/processed/multi100_master_processed_data.csv"))

readr::write_csv(original_effect_sizes, here::here("data/processed/multi100_original_effect-sizes_processed_data.csv"))

readr::write_csv(reanalyzed_effect_sizes, here::here("data/processed/multi100_reanalyzed_effect-sizes_processed_data.csv"))
```

## Peer evaluation data

Add peereval_submission_number.

```{r}
peer_eval <-
  peer_eval |> 
  mutate(
    peereval_submission_number = 1:nrow(peer_eval),
    # create eval_id which concatenates analyst_id, paper_id, and evaluator_id
    eval_id = paste(analyst_id, paper_id, evaluator_id, sep = "_")
    )
```

We pay attention to the first 500 peer evaluations only.

```{r}
peer_eval <- 
  peer_eval |> 
  slice(1:500)
```

Remove 'OTHER' submission - evaluator did not provide the ID of the co-analyst and so should be removed for now.
This is submission number 459.

```{r}
peer_eval <- 
  peer_eval |> 
  filter(peereval_submission_number != 459) # flag this to count it in the results paper
```

We changed non-unique analyst_ids in the main dataset (multi100_data), now we change the corresponding ids in the peer_eval data as well.

```{r}
peer_eval <-
  peer_eval |> 
  mutate(analyst_id = case_when(
    analyst_id == "MX02W" ~ "EZI7J",
    TRUE ~ analyst_id
  ))
```

Check that all evaluator_id's appear in multi100_data$analyst_id. If 'FALSE' then all ID's match.

```{r}
any(!peer_eval$evaluator_id %in% multi100_data$analyst_id)
```

Check that all analyst_id's appear in multi100_data$analyst_id. If 'FALSE' then all ID's match.

```{r}
any(!peer_eval$analyst_id %in% multi100_data$analyst_id)

peer_eval |> 
  filter(!analyst_id %in% multi100_data$analyst_id)
```

Check that all paper_id's appear in multi100_data$paper_id. If 'FALSE' then all ID's match.

```{r}
any(!peer_eval$paper_id %in% multi100_data$paper_id)
```

Check with setdiff that all of the analyst_id and paper_id pairs in PeerEvals appear in multi100_data.

```{r}
setdiff(
  dplyr::select(peer_eval, analyst_id, paper_id),
  dplyr::select(multi100_data, analyst_id, paper_id)
  )
```

Fixing erroneous ids:
* AUX74_Bursztyn_JournPoliEco_2012_jaK4 (SN. 141): should be AUX74_Bursztyn_AmEcoRev_2017_VB9K
* UNX4S_Bursztyn_AmEcoRev_2017_VB9K (SN. 208): should be UNX4S_Bursztyn_JournPoliEco_2012_jaK4
* CCU09_Baillon_Econometrica_2018_QYNq (SN. 284): should be CC3UD_Baillon_Econometrica_2018_QYNq - analyst describes that the analyst does not provide their code. This is the case for CC3UD (similar to CCU09) on the Baillon paper.
* 8GS2H_Hurst_EvoHumanBehavior_2017_yypJ (SN. 333): should be 8GS27_Hurst_EvoHumanBehavior_2017_yypJ
* QPS9D_Bigoni_Econometrica_2015_VBx1 (two cases) (SN. 343, 352): should be QPSID_Bigoni_Econometrica_2015_VBx1 - both QPS9D and QPSID exist as separate analysts
* J3ODA_Sliwka_JournLabEco_2017_VDJV (SN. 350): should be JE3RS_Sliwka_JournLabEco_2017_VDJV - similar ID exists on sliwka OSF page... two other analysts evaluated J3ODA, both for a different paper (Nyhan)... evaluator here states that they found evidence for the null hypothesis, which is the case in the submission of JE3RS_Sliwka (and this is different to the two other evaluations)
* 0XXWZ_Kucik_BritJournPoliSci_2016_L22B (SN. 406): should be 0XXW0_Kucik_BritJournPoliSci_2016_L22B - there exists a 0XXWZ_BATESON, but on the Kucik page the ID is 0XXW0
* DAIUV_Jiang_AmJourPoliSci_2018_Rjp9 (two cases) (SN. 446, 451): should be DAILV_Jiang_AmJourPoliSci_2018_Rjp9 - DAIUV_Baillon exists, DAILV_Rovny exists and DAILV_2_Jiang exists (mislabelled on OSF)
* SN. 446 submitted the co-analysts ID as their own ID - it should be NSDML (based on the email address they provided)

Alter either the analyst_id or paper_id as appropriate.
TODO: change the ids to actual text for safety
```{r}
peer_eval <-
  peer_eval %>%
  mutate(
    paper_id = case_when(
      peereval_submission_number == 141 ~ "Bursztyn_AmEcoRev_2017_VB9K",
      peereval_submission_number == 208 ~ "Bursztyn_JournPoliEco_2012_jaK4",
      TRUE ~ paper_id
    ),
    analyst_id = case_when(
      peereval_submission_number == 284 ~ "CC3UD",
      peereval_submission_number == 333 ~ "8GS27",
      peereval_submission_number == 343 ~ "QPSID",
      peereval_submission_number == 352 ~ "QPSID",
      peereval_submission_number == 350 ~ "JE3RS",
      peereval_submission_number == 406 ~ "0XXW0",
      peereval_submission_number == 446 ~ "DAILV",
      peereval_submission_number == 451 ~ "DAILV",
      TRUE ~ analyst_id
    ),
    evaluator_id = case_when(peereval_submission_number == 446 ~ "NSDML",
                             TRUE ~ evaluator_id)
  )
```

We have to change these values in the peer eval review as well.

```{r}
peer_eval_review <- 
  peer_eval_review |> 
  mutate(
    analyst_id = case_when(
      analyst_id == "J3ODA" & paper_id == "Sliwka_JournLabEco_2017_VDJV" & evaluator_id == "A1SBQ" ~ "JE3RS",
      TRUE ~ analyst_id
    )
  ) |> 
  # We also drop some of the values that are duplicates and should not be in the peer evaluation review
  filter(
    !(analyst_id == "GHN4R" & paper_id == "Menaldo_AmJourPoliSci_2016_Vx4e" & evaluator_id == "WANJC"),
    !(analyst_id == "MOYDE" & paper_id == "Axt_JournExpSocPsych_2018_zK2" & evaluator_id == "EZI7J")
    )
```

Re-run code to produce eval_id.

```{r}
peer_eval <-
  peer_eval |> 
  mutate(
    eval_id = paste(analyst_id, paper_id, evaluator_id, sep = "_")
    )
```

Verify that all paper_id and analyst_id combinations now appear in multi100_data.

```{r}
setdiff(
  dplyr::select(peer_eval, paper_id, analyst_id),
  dplyr::select(multi100_data, paper_id, analyst_id)
  )
```

Check and remove duplicate responses.

```{r}
peer_eval_duplicates <-
  peer_eval |> 
  group_by(eval_id) |> 
  mutate(n = n()) |> 
  filter(n > 1) |> 
  arrange(desc(n))

peer_eval_duplicates |> 
  distinct(eval_id, n)
```

Duplicated peer evals are the following:
* WCZJU_Luttrell_JournExpSocPsych_2016_rjb_EZI7J: !SN. 17
* MOYDE_Axt_JournExpSocPsych_2018_zK2_EZI7J: !SN. 45
* PFQSU_Miller_JournConflictRes_2011_zV1O_AMDFX: !SN. 103
* CC3UD_Baillon_Econometrica_2018_QYNq_AHW5W: !SN. 284
* 67DKH_Ihme_JournExpPoliSci_2018_xYbO_R08MV: !SN. 298
* 9U4RV_Hou_ChildDev_2017_YOXl_EZI7J: !SN. 355
* Q5U26_Wang_AmEcoJourn_2013_7d4J_SJAS8: !SN. 375
* GHN4R_Menaldo_AmJourPoliSci_2016_Vx4e_WANJC: !SN. 465, 466

Deleting duplicates.

```{r}
peer_eval <-
  peer_eval |> 
  filter(
    peereval_submission_number != 17,
    peereval_submission_number != 45,
    peereval_submission_number != 103,
    peereval_submission_number != 284,
    peereval_submission_number != 298,
    peereval_submission_number != 355,
    peereval_submission_number != 375,
    peereval_submission_number != 465,
    peereval_submission_number != 466
  )
```

Remove case where evaluator reviewed their own analysis (!SN. 462: WJVLO_Pastötter_Cognition_2013_EQxa_WJVLO). We decided to treat this responses as non-valid response and do not include it in the summary statistics for the peer evaluation in the results section of the paper.

```{r}
peer_eval <-
  peer_eval |> 
  filter(peereval_submission_number != 462)
```

Count the number of times each paper_id and analyst_id appears in peer_eval.

```{r}
peer_eval %>%
  count(paper_id, analyst_id) |> 
  arrange(desc(n))
```

Transforming peer evaluation responses based on the review by the expert panel. We will make two version of the peer evaluation dataset for the analysis:
* One that contains all the peer evaluation data preprocessing steps except the changed responses due to the review of the peer evaluation: multi100_peer-eval-not-reviewed_processed_data
* One that contains all data preprocessing steps AND the changed values as well: multi100_peer-eval_processed_data

```{r}
# Filter values to be changed by the peer evalution review
# Decision for values to be changed were done by the core team
peer_eval_to_change <-
  peer_eval_review |>
  dplyr::select(evaluator_id, paper_id, analyst_id, variable_name, change_to) |>
  filter(!is.na(change_to))

peer_eval_changed <-
  peer_eval %>%
  pivot_longer(cols = c(-analyst_id, -paper_id, -evaluator_id, -peereval_timestamp, -peereval_submission_number, -eval_id, -evaluator_comments), names_to = "variable_name") %>%
  left_join(
    .,
    peer_eval_to_change,
    by = c("evaluator_id", "paper_id", "analyst_id", "variable_name")
    ) %>%
  mutate(value = if_else(!is.na(change_to), change_to, value)) %>%
  dplyr::select(-change_to) %>%
  pivot_wider(names_from = variable_name, values_from = value)
```

According to the decision of the expert panel `r nrow(peer_eval_changed)` decisions made by the peer evaluators were modified.

Save processed peer evaluation and peer evaluation review data separately.

```{r}
write_csv(peer_eval_changed, here::here("data/processed/multi100_peer-eval_processed_data.csv"))

write_csv(peer_eval, here::here("data/processed/multi100_peer-eval-not-reviewed_processed_data.csv"))

write_csv(peer_eval_review, here::here("data/processed/multi100_peer-eval-review_processed_data.csv"))
```

